Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions

### 2015-01-28 HGmodelMANUSCRIPT/HGmodel_draft3.tex
Added table ranking the force fields at full hydration.

To get a general idea of the quality of the glycerol backbone and choline headgroup structures in different models, we calculated the absolute
values of the order parameters for these parts from fourteen different lipid models (Table~\ref{systems}) and 
plotted the results together with experimental values in Fig.~\ref{HGorderparameters}.
Two criteria were used to judge the quality of the model: there must not be significant  {\bf forking} in the $\alpha$ and $\beta$ carbons,
there must be only moderate forking in the g$_3$ carbon and there must be significant forking in the g$_1$ carbon, {\bf absolute values}
should be preferably inside to the subjective sweet spots determined from experiments (blue shaded regions in Fig.~\ref{HGorderparameters}).
None of the studied force fields fulfils these criteria. However, three force fields perform better than others, namely CHARMM36~\cite{klauda10}, MacRog~\cite{maciejewski14} and GAFFlipid~\cite{dickson12}.
The results for each force field in respect to the above criteria are summarized in Table~\ref{??} \todo{This kind of table should be done or not?}.

>>>>

To get a general idea of the quality of the glycerol backbone and choline headgroup structures in different models, we calculated the absolute
values of the order parameters for these parts from fourteen different lipid models (Table~\ref{systems}) and 
plotted the results together with experimental values in Fig.~\ref{HGorderparameters}.
Two criteria were used to judge the quality of the model: there must not be significant  {\bf forking} in the $\alpha$ and $\beta$ carbons,
there must be only moderate forking in the g$_3$ carbon and there must be significant forking in the g$_1$ carbon, {\bf absolute values}
should be preferably inside to the subjective sweet spots determined from experiments (blue shaded regions in Fig.~\ref{HGorderparameters}).
None of the studied force fields fulfils these criteria. However, three force fields perform better than others, namely CHARMM36~\cite{klauda10}, MacRog~\cite{maciejewski14} and GAFFlipid~\cite{dickson12}.
The results for each force field in respect to the above criteria are summarized in Figure~\ref{FullHydrationComparisonTable}.
\todo{This kind of table should be done or not? DONE, see Fig.~\ref{FullHydrationComparisonTable}}.
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/comparisonTable.pdf}
  \caption{\label{FullHydrationComparisonTable}
  Ranking of force fields based on data of Fig.~\ref{HGorderparameters}.
  } 
\end{figure}
